Dimensions of the impacts of land transitions in the Amazon and Cerrado

### 2023-02-07 manuscript/lct_se_ac.qmd
Add content to the literature review methods.

---
title: "Dimensions of the impacts of land transitions in the Amazon and Cerrado"
author: 
  - name: Hugo Tameirão Seixas
    email: seixas.hugo@protonmail.com
    url: hugotseixas.com
    affiliations:
      - name: State University of Campinas
format: 
  html:
    theme: lux
page-layout: article
bibliography: references.bib
link-citations: true
editor: visual
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto
  cache: true
license: CC BY-NC-ND 4.0
---

@@

  graph [layout = dot, 
         rankdir = TD, 
         nodesep = 1.5, 
         ranksep = 1.0,
         tooltip = ' ']

@@

The literature overview will be performed over different subjects.

>>>>

---
title: "Dimensions of the impacts of land transitions in the Amazon and Cerrado"
author: 
  - name: Hugo Tameirão Seixas
    email: seixas.hugo@protonmail.com
    url: hugotseixas.com
    affiliations:
      - name: State University of Campinas
format: 
  html:
    theme: lux
page-layout: article
bibliography: references.bib
link-citations: true
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto
license: CC BY-NC-ND 4.0
---

@@

  graph [layout = dot, 
         rankdir = TD, 
         nodesep = 1.2, 
         ranksep = 0.8,
         tooltip = ' ']

@@

The literature overview will be performed over different subjects. For all of them, an hybrid approach will be adopted, in which database searches are combined with snowball searches.

  graph [layout = dot, 
         overlap = false,
         rankdir = TB, 
         nodesep = 5, 
         ranksep = 0.4,
         tooltip = ' ']

  a [label = 'Specific \n Questions']
  b [label = 'Query \n Development']
  c [label = 'Database Search']
  d [label = 'Documents \n Screening']
  e [label = 'Documents \n Collection']
  f [label = 'Forward Snowball \n Search']
  g [label = 'Final Collection']

  a -> b a -> d
  b -> c c -> d
  d -> e e -> f
  f -> d e -> g
